Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
more benchmarks description

%\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }

@@

The safety property represented by $\phi_{safety}$ is encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
\end{equation}
%
%\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
This means that the states will always be within the $n$-dimensional 
hyper-box, which is typically defined by the safety specification.

@@

   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesize};

@@

\begin{figure}[htb]
{\scriptsize
\centering
%\resizebox{.8\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=8cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc 2.Safety}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc 3.Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc 4.Complete}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Completeness\\Verifier};
   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
   }   
    \\
  };

@@

In order to compute the set of reachable states we find 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not be violated for any $k>\overline{k}$. 
The closed-loop state-space system has to be unwound up to a given 
depth $\overline{k}$ to ensure that $\phi_{safety}$ holds.

@@

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}
and consists of five stages, as described below:

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$.

2. The validation phase consists of four stages 
(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
performs potentially unsound
operations assuming a plant's precision $<I_p,F_p>$, 
current $k$ and sampling rate, whereas the subsequent three stages are used to 
restore soundness.

3. This stage restores soundness with respect to the plant precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage.

4. This stage checks that the current  $k$ 
is large enough to ensure that the boundaries are not be violated for any $k'>k$.
In order to verify this, we compute the 
completeness threshold $\overline{k}$ for the current candidate $K$ 
and check that $k{\leq}\overline{k}$.

5. The last stage ensures that the current sampling rate is large enough by using an 
external checker (\todo{add more details here once we have them}).

@@

Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}. \textit{DC Motor Position} plant provides the rotary motion that coupled with wheels and cables provides translational motion. \textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension only. \textit{Ball Magnetic Levitation} plant describes the magnetic field that keeps a metal ball hanged in air.

These benchmarks were discretized with different sample times using the approach described in Appendix ~\ref{sec:appendix}. All the experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.

>>>>

\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }

@@

The safety property represented by $\phi_{safety}$ is encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
\end{equation}
%
\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}

where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
This means that the states will always be within the $n$-dimensional 
hyper-box, which is typically defined by the safety specification.

@@

   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesise};

@@

\begin{figure}[htb]
{\scriptsize
\centering
%\resizebox{.8\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=8cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Complete}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Sampling}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Completeness\\Verifier};
   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
   }   
    \\
  };

@@

In order to compute the set of reachable states we find 
a completeness threshold $k_{bound}$.
Essentially, $k_{bound}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not be violated for any $k>k_{bound}$. 
The closed-loop state-space system has to be unwound up to a given 
depth $k_{bound}$ to ensure that $\phi_{safety}$ holds.

@@

\todo{Describe each step in Fig~\ref{fig:CEGIS-precision-increment}.}

@@

Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}. \textit{DC Motor Position} plant describes the rotary motion that coupled with wheels and cables provides translational motion. \textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension. \textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a metal ball hanged in air. \textit{Buck Converter} plant represents a power converter that steps down voltage from the supply to the load while stepping up current. \textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current. \textit{Buck-boost Converter} plant is a particular type of converter that has an output voltage magnitude that is either greater than or less than the input voltage magnitude. \textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle.
